---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CTVsuggestTrain

<!-- badges: start -->
<!-- badges: end -->

**CTVsuggestTrain** carries out the model building and creates the `data.frame` containing the classification probabilities outputted by the [**CTVsuggest**](https://dylandijk.github.io/CTVsuggest/index.html) package.


The **CTVsuggestTrain** package has a single exported function: `Train_model()`, that constructs features and trains a multinomial logistic regression model with the objective of classifying CRAN packages to available [CRAN Task Views](https://github.com/cran-task-views/ctv#available-task-views). For further a more detailed description of the model, view the [Model Section](https://dylandijk.github.io/CTVsuggest/articles/Package-Overview.html#the-model) of the [CTVsuggest Overview Vignette](https://dylandijk.github.io/CTVsuggest/articles/CTVsuggest-Overview.html).

The `Train_model()` function takes a while to run, on my machine (*Windows Intel(R) Core(TM) i5-10210U CPU @ 1.60GHz, 2112 Mhz, 4 Cores, 8 Logical Processors*) it takes 30 minutes.

---

Important to note that in order to output suggestions using the **CTVsuggest** package, you can completely ignore the **CTVsuggestTrain** package. I will use this package to train the model weekly in order to keep it up to date. Having this code packaged makes it easier for me to carry out model training, and makes the model building transparent for others to inspect how it is carried out.

For further detail on the workflow view the [Packages Workflow Section](https://dylandijk.github.io/CTVsuggest/articles/CTVsuggest-Overview.html#the-package-workflow) of the [CTVsuggest Overview Vignette](https://dylandijk.github.io/CTVsuggest/articles/CTVsuggest-Overview.html).


## Installation

You can install the development version of CTVsuggestTrain from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("DylanDijk/CTVsuggestTrain")
```

## Example

The following code saves the model, model accuracy and `data.frame` containing classification probabilities for packages to an `"OUTPUT"` directory in your current working directory.

```{r example, eval=FALSE}
library(CTVsuggestTrain)
Train_model(save_output = TRUE, save_path = "OUTPUT/")
```


The code example above is the code I run to retrieve an up to date model.
