---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CTVsuggestTrain

<!-- badges: start -->
<!-- badges: end -->

**CTVsuggestTrain** carries out the model building and creates the `data.frame` containing the classification probabilities outputted by the [**CTVsuggest**](https://dylandijk.github.io/CTVsuggest/index.html) package.

The **CTVsuggestTrain** package has a single exported function: `Train_model()`, that constructs features and trains a multinomial logistic regression model with the objective of classifying CRAN packages to available [CRAN Task Views](https://github.com/cran-task-views/ctv#available-task-views). For further a more detailed description of the model, view the [Model Section](https://dylandijk.github.io/CTVsuggestTrain/articles/Package-Overview.html#the-model) of the [CTVsuggest Overview Vignette](https://dylandijk.github.io/CTVsuggest/articles/CTVsuggest-Overview.html).

The `Train_model()` function takes a while to run, on my machine (add specs) it takes 30 minutes. 


## Installation

You can install the development version of CTVsuggestTrain from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("DylanDijk/CTVsuggestTrain")
```

## Example

The following code saves the model, model accuracy and `data.frame` containing classification probabilities for packages to an `"OUTPUT"` directory in your current working directory.

```{r example, eval=FALSE}
library(CTVsuggestTrain)
Train_model(save_output = TRUE, save_path = "OUTPUT/")
```

